Path Analysis Data Development - Chapter 2

### 2016-02-09 sem__data_development.Rmd
Update and rename path model data.

>>>>

### Update path analysis data
Updating the path analysis data with the temperature during wet days variables.
```{r update data}
load("pathmodel_data_20160112.RData")
wet_hrs <- read.csv("analysis/data/wet-days-temperature-variables.csv")
save.image("~/GitHub/superspreaders/pathmodel_data.RData")
```
